Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-28 appendix.tex
Update appendix template with the one provided by SC

Reproducibility initiative appendices: Artifact Description (AD) and Computational Results Analysis (CRA). Description of the organization of the appendix.

@@

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 17}
\label{apndx:fig16}

>>>>

% -----------------------------------------------------------------------------
\subsection{Abstract}

\input{abstract}

% -----------------------------------------------------------------------------
\subsection{Description}

% -----------------------------------------------------------------------------
\subsubsection{Check-list (artifact meta information)}

{\small
\begin{itemize}
%  \item {\bf Algorithm: }
  \item {\bf Program: ATLAS Monte Carlo Workflow, Geant4, AthenaMP, GROMACS}
%  \item {\bf Compilation: }
%  \item {\bf Transformations: }
%  \item {\bf Binary: }
  \item {\bf Data set: Available at \\ \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/tree/master/data}}
  \item {\bf Run-time environment: PanDA Workload Management System, RADICAL-Pilot Pilot System (NGE)}
  \item {\bf Hardware: OLCF Titan Cray XK7}
%  \item {\bf Run-time state: }
%  \item {\bf Execution: }
  \item {\bf Output: Available at \\ \url{https://github.com/ATLAS-Titan/PanDA-WMS-paper/tree/master/data}}
  \item {\bf Experiment workflow: Raw data acquisition, data wrangling and filtering, plotting, analysis}
%  \item {\bf Experiment customization: }
  \item {\bf Publicly available?: Yes}
\end{itemize}
}

% -----------------------------------------------------------------------------
\subsubsection{How software can be obtained (if available)}

\begin{itemize}
    \item PanDA Workload Management System: \\ \url{https://github.com/PanDAWMS}.
    \item RADICAL-Pilot Pilot System (NGE): \\ \url{https://github.com/radical-cybertools}.
\end{itemize}

% -----------------------------------------------------------------------------
\subsubsection{Hardware dependencies}

Access and allocation on OLCF Titan Cray XK7, workstation with at least 8GB of RAM.

% -----------------------------------------------------------------------------
\subsubsection{Software dependencies}

Python, jupyter, pandas, matplotlib, gnuplot, excel.

% -----------------------------------------------------------------------------
\subsubsection{Datasets}

\begin{description}[align=left]
    \item [Section 5.1 -- Figure 3] \url{}
    \item [Section 5.1 -- Figure 4] \url{}
    \item [Section 5.1 -- Figure 5] \url{}
    \item [Section 5.1 -- Figure 6] \url{}
    \item [Section 5.2 -- Figure 7] \url{}
    \item [Section 5.2 -- Figure 8] \url{}
    \item [Section 5.3 -- Figure 9] \url{}
    \item [Section 6.3 -- Figure 14] \url{}
    \item [Section 6.3 -- Figure 15] \url{}
    \item [Section 6.3 -- Figure 16] \url{}
    \item [Section 6.3 -- Figure 17] \url{}
    \item [Section 6.3 -- Figure 18] \url{}
    \item [Section 6.3 -- Figure 19] \url{}
    \item [Section 6.3 -- Figure 20] \url{}
    \item [Section 6.3 -- Figure 21] \url{}
\end{description}

% -----------------------------------------------------------------------------
\subsection{Installation}

\begin{description}[align=left]
    \item [Section 5.1 -- Figure 3] \url{}
    \item [Section 5.1 -- Figure 4] \url{}
    \item [Section 5.1 -- Figure 5] \url{}
    \item [Section 5.1 -- Figure 6] \url{}
    \item [Section 5.2 -- Figure 7] \url{}
    \item [Section 5.2 -- Figure 8] \url{}
    \item [Section 5.3 -- Figure 9] \url{}
    \item [Section 6.3 -- Figure 14] \url{}
    \item [Section 6.3 -- Figure 15] \url{}
    \item [Section 6.3 -- Figure 16] \url{}
    \item [Section 6.3 -- Figure 17] \url{}
    \item [Section 6.3 -- Figure 18] \url{}
    \item [Section 6.3 -- Figure 19] \url{}
    \item [Section 6.3 -- Figure 20] \url{}
    \item [Section 6.3 -- Figure 21] \url{}
\end{description}

% -----------------------------------------------------------------------------
\subsection{Experiment workflow}

\begin{description}[align=left]
    \item [Section 5.1 -- Figure 3] \url{}
    \item [Section 5.1 -- Figure 4] \url{}
    \item [Section 5.1 -- Figure 5] \url{}
    \item [Section 5.1 -- Figure 6] \url{}
    \item [Section 5.2 -- Figure 7] \url{}
    \item [Section 5.2 -- Figure 8] \url{}
    \item [Section 5.3 -- Figure 9] \url{}
    \item [Section 6.3 -- Figure 14] \url{}
    \item [Section 6.3 -- Figure 15] \url{}
    \item [Section 6.3 -- Figure 16] \url{}
    \item [Section 6.3 -- Figure 17] \url{}
    \item [Section 6.3 -- Figure 18] \url{}
    \item [Section 6.3 -- Figure 19] \url{}
    \item [Section 6.3 -- Figure 20] \url{}
    \item [Section 6.3 -- Figure 21] \url{}
\end{description}

% -----------------------------------------------------------------------------
\subsection{Evaluation and expected result}

\begin{description}[align=left]
    \item [Section 5.1 -- Figure 3] \url{}
    \item [Section 5.1 -- Figure 4] \url{}
    \item [Section 5.1 -- Figure 5] \url{}
    \item [Section 5.1 -- Figure 6] \url{}
    \item [Section 5.2 -- Figure 7] \url{}
    \item [Section 5.2 -- Figure 8] \url{}
    \item [Section 5.3 -- Figure 9] \url{}
    \item [Section 6.3 -- Figure 14] \url{}
    \item [Section 6.3 -- Figure 15] \url{}
    \item [Section 6.3 -- Figure 16] \url{}
    \item [Section 6.3 -- Figure 17] \url{}
    \item [Section 6.3 -- Figure 18] \url{}
    \item [Section 6.3 -- Figure 19] \url{}
    \item [Section 6.3 -- Figure 20] \url{}
    \item [Section 6.3 -- Figure 21] \url{}
\end{description}

% ----------------------------------------------------------------------------- % \subsection{Experiment customization}

% -----------------------------------------------------------------------------
% \subsection{Notes}

% =============================================================================
\section{OLD -- REMOVE AFTER COMPLETING ABOVE}
Reproducibility initiative appendices: Artifact Description (AD) and Computational Results Analysis (CRA). Description of the organization of the appendix.

@@

% -----------------------------------------------------------------------------
\subsection{Section 6.3 - Figure 16}
\label{apndx:fig16}

### 2017-03-28 paper.tex
First iteration appendix template
Fix Appendix numbering
Update appendix template with the one provided by SC

%Conference
\acmConference[SC2017]{The International Conference for High Performance Computing, Networking, Storage and Analysis}{Nov 2017}{Denver, Colorado}
\acmYear{2017}
\copyrightyear{2017}

@@

>>>>

%Conference
\acmConference[SC2017]{The International Conference for High Performance Computing, Networking, Storage and Analysis}{Nov 2017}{Denver, Colorado, USA}
\acmYear{2017}
\copyrightyear{2017}

@@

% ----------------------------------------------------------------------------
% APPENDIX
% ----------------------------------------------------------------------------
\appendix
\section{Artifact Description --- Converging High-Throughput and High-Performance Computing: A Case Study}
\label{apnx:ac}

\input{appendix}
